---
title: "Using a Parsnip Model to Fit and Predict Logistic Lasso"
subtitle: "STA314, Fall 2020"
author: "Ziyue Yang"
date: "November 27^th^, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("functions.R")
source("make_tidy.R")
```

# Intoduction

To use the model in this article, you will need to install package `tidymodels`.

This model allows us to fit and predict a logistic lasso with chosen parameters.

# Using the Model

```{r}
n <- 1000
lambda <- 0.3

dat <- tibble(x = seq(-3,3, length.out = n),
              w = 3*cos(3*seq(-pi,pi, length.out = n)),
              y = rbinom(n,size = 1, prob = 1/(1 + exp(-w+2*x)) )%>% as.numeric %>% factor,
              lambda = 0.3,
              cat = sample(c("a","b","c"), n, replace = TRUE)
)
split <- initial_split(dat, strata = c("cat"))
train <- training(split)
test <- testing(split)
rec <- recipe(y ~ . , data = train) %>% step_dummy(all_nominal(), -y) %>% step_zv(all_outcomes()) %>% 
  step_normalize(all_numeric(), -y) %>%
  step_intercept()

spec <- PIRLS() %>% set_engine("fit_logistic_lasso")
  
fit <- workflow() %>% add_recipe(rec) %>% add_model(spec) %>% fit(train)
predict(fit, new_data = test) %>% bind_cols(test %>% select(y)) %>% conf_mat(truth = y, estimate = .pred_class)


```


---

# Functions Behind the Model

Let's begin with the function `fit_logistic_lasso`, which, as its name refers to,
fits a logistic lasso, based on the following inputs:

* `x`: A matrix of predictors that does not include intercepts.
* `y`: A vector of data.
* `lambda`: The penalty term.
* `beta0`: Initial guess of $\beta$.
* `eps`: Parameter for stopping criterion.
* `iter_max`: Maximum number of iterations.

The function `fit_logistic_lasso` returns a list containing three terms: the intercept (`intercept`), beta (`beta`), and lambda (`lambda`).

Here's how the function works: after the inputs have been taken, we update $\beta$ for $n$ times, where $n$ is the integer input of `iter_max`. 
